
```{r}
#TRANSFORM DATA FROM WIDE TO LONG
# Load necessary libraries
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(tidyverse)
file_path <- "/Users/nene/Desktop/GALI_External_DataRelease_2020.xlsx"
Gali_data <- read_excel(file_path, sheet = "Data")

```

```{r}

library(dplyr)
library(tidyr)
library(stringr)

df_long <- Gali_data %>%
  mutate(across(everything(), as.character)) %>%
  select(New_External_ID, participated, program_year, matches("^fu[1-4]")) %>%
  pivot_longer(
    cols = starts_with("fu"),
    names_to = "name",
    values_to = "value"
  ) %>%
  mutate(
    time = as.numeric(str_extract(name, "(?<=fu)[1-4]")),
    variable = str_remove(name, "fu[1-4]"),
    year = time + 2018
  ) %>%
  select(-name) %>%
  filter(
    !is.na(value),
    value != "",
    !str_detect(value, "^5+$")
  )


```



```{r}
# Create a "years_since_joining" variable (will be NA for non-accelerator ventures)
df_long <- df_long %>%
  mutate(
    year = as.numeric(year),
    program_year = as.numeric(program_year),  # convert this too
    years_since_joining = ifelse(!is.na(program_year) & !is.na(year),
                                 year - program_year,
                                 NA_real_)
  )



# Add post_accelerator variable
df_long <- df_long %>%
  mutate(
    post_accelerator = ifelse(participated == 1 & year >= program_year, TRUE, FALSE)
  )

# Step 1: Select just the ID and program_region from Gali_data
region_data <- Gali_data %>%
  select(New_External_ID, program_region)

# Step 2: Join this with df_long using a left join
df_region <- df_long %>%
  left_join(region_data, by = "New_External_ID")

```


```{r}
#  SAME BUT NEW Load libraries
library(lme4)
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)

# --------------------------
# 1. Data Preprocessing
# --------------------------

# Financial Performance Data
df_perform <- df_region %>%
  mutate(
    fins_revenues_m1 = case_when(
      variable == "fins_revenues_m1" ~ as.numeric(value),
      TRUE ~ NA_real_
    ),
    wages = case_when(
      variable == "fins_wages_m1" ~ as.numeric(value),
      TRUE ~ NA_real_
    ),
    profit_category = case_when(
      variable == "fins_profit_m1" & str_detect(value, "Negative ROI") ~ "loss",
      variable == "fins_profit_m1" & str_detect(value, "Not applicable") ~ "NA",
      variable == "fins_profit_m1" & str_detect(value, "Unsure") ~ "neutral",
      variable == "fins_profit_m1" & str_detect(value, "0% - 5%|6% - 10%|11% - 15%|16% - 20%|More than 20%") ~ "profit",
      TRUE ~ NA_character_
    )
  )

# Set levels explicitly
df_perform$profit_category <- factor(df_perform$profit_category, levels = c("loss", "neutral", "profit"))

# Employment Data
df_emplo <- df_region %>%
  mutate(
    fulltime = case_when(variable == "fins_ft_employees_m1" ~ as.numeric(value), TRUE ~ NA_real_),
    parttime = case_when(variable == "fins_pt_employees_m1" ~ as.numeric(value), TRUE ~ NA_real_)
  ) %>%
  filter(!is.na(fulltime) | !is.na(parttime)) %>%
  group_by(New_External_ID) %>%
  summarise(
    fulltime = sum(fulltime, na.rm = TRUE),
    parttime = sum(parttime, na.rm = TRUE),
    FTE = fulltime + (parttime * 0.5),
    program_region = first(program_region),
    participated = first(participated),
    years_since_joining = first(years_since_joining),
    post_accelerator = first(post_accelerator),
    year = first(year),
    .groups = "drop"
  )

# Investment Data
df_Invest <- df_region %>%
  mutate(
    Accel = case_when(variable == "inv_equityfrom_accelerators" ~ as.numeric(value), TRUE ~ NA_real_),
    Venture = case_when(variable == "inv_equityfrom_venturecap" ~ as.numeric(value), TRUE ~ NA_real_),
    Own = case_when(variable == "inv_ownmoney_m1" ~ as.numeric(value), TRUE ~ NA_real_),
    Outequity = case_when(variable == "inv_outequity_m1" ~ as.numeric(value), TRUE ~ NA_real_),
     Debt = case_when(
      variable == "inv_totaldebt_m1" ~ suppressWarnings(as.numeric(value)),
      TRUE ~ NA_real_
    ),
    Phil = case_when(
      variable == "inv_philan_m1" ~ suppressWarnings(as.numeric(value)),
      TRUE ~ NA_real_))

   

# --------------------------
# 2. Regressions
# --------------------------

# Common function to relevel and log-transform
prepare_data <- function(df, varname) {
  df$program_region <- relevel(factor(df$program_region), ref = "North America")
  df[[paste0("log_", varname)]] <- log(df[[varname]] + 1)
  return(df)
}

# Revenue
df_perform <- prepare_data(df_perform, "fins_revenues_m1")
model_logREV <- lmer(log_fins_revenues_m1 ~ participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_perform)



# Wages
df_perform <- prepare_data(df_perform, "wages")
model_logWAG <- lmer(log_wages ~  participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_perform)

# Employees (linear, not mixed model)
df_emplo$program_region <- relevel(factor(df_emplo$program_region), ref = "North America")
model_logEMP1 <- lm(FTE ~  participated * post_accelerator + years_since_joining + program_region, data = df_emplo)

# Venture (binary logistic)
df_Invest$program_region <- relevel(factor(df_Invest$program_region), ref = "North America")
df_Invest$Venture_bin <- as.numeric(as.character(df_Invest$Venture))
model_glm_venture <- glm(Venture_bin ~  participated * post_accelerator + years_since_joining + program_region, data = df_Invest, family = binomial(link = "logit"))

# Own Investment
df_Invest <- prepare_data(df_Invest, "Own")
model_logOWN <- lmer(log_Own ~  participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_Invest)

# Outequity
df_Invest <- prepare_data(df_Invest, "Outequity")
model_logOUT <- lmer(log_Outequity ~  participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_Invest)

# Debt
df_Invest <- prepare_data(df_Invest, "Debt")
model_logDEBT <- lmer(log_Debt ~  participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_Invest)

# Philanthropy
df_Invest <- prepare_data(df_Invest, "Phil")
model_logPhil <- lmer(log_Phil ~  participated * post_accelerator + years_since_joining + program_region + (1 | New_External_ID), data = df_Invest)


# --------------------------
# 3. View Summaries
# --------------------------
list(
  Revenue = summary(model_logREV),
  Wages = summary(model_logWAG),
  Employees = summary(model_logEMP1),
  Venture = summary(model_glm_venture),
  Own_Money_Invested = summary(model_logOWN),
  Outequity = summary(model_logOUT),
  Debt = summary(model_logDEBT),
  Philanthropy = summary(model_logPhil))
 

```




```{r}
library(scales)  # Add this line


ggplot(df_perform %>% 
         filter(!is.na(years_since_joining),
                !is.na(program_region),
                str_to_lower(program_region) != "other"),  # Exclude "other"
       aes(x = years_since_joining, y = fins_revenues_m1, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_continuous(labels = label_comma(), trans = "log10") +  # Log scale
  labs(title = "Revenue in Dollars Since Joining (Participated vs Non-Participated)",
       y = "Revenue",
       x = "Years Since Joining (0 = join year, negative = before joining)",
       color = "Participation Status") +
  scale_color_manual(values = c("steelblue", "darkorange"),
                     labels = c("Non-Participant", "Participant")) +
  theme_minimal() +
  facet_wrap(~ program_region, scales = "free_y") +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )


ggplot(df_perform %>% 
         filter(!is.na(years_since_joining),
                !is.na(program_region),
                str_to_lower(program_region) != "other"),  # Exclude "other"
       aes(x = years_since_joining, y = wages, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_continuous(labels = label_comma(), trans = "log10") +  # Log scale
  labs(title = "Wages in Dollars Since Joining (Participated vs Non-Participated)",
       y = "Wages",
       x = "Years Since Joining (0 = join year, negative = before joining)",
       color = "Participation Status") +
  scale_color_manual(values = c("steelblue", "red"),
                     labels = c("Non-Participant", "Participant")) +
  theme_minimal() +
  facet_wrap(~ program_region, scales = "free_y") +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )


```

```{r}
#You can create an approximate FTE column on your own table simply by multiplying your FT head‑count by 1.0 and your PT head‑count by your chosen weight (say 0.5), then summing. For example, in R (using dplyr) you could do:


library(dplyr)
library(tidyr)

df_emplo <- df_region %>%
  mutate(
    fulltime = case_when(
      variable == "fins_ft_employees_m1" ~ as.numeric(value),
      TRUE ~ NA_real_
    ),
    parttime = case_when(
      variable == "fins_pt_employees_m1" ~ as.numeric(value),
      TRUE ~ NA_real_
    )
  ) %>%
  # Filter to keep rows where at least one is non-NA
  filter(!is.na(fulltime) | !is.na(parttime)) %>%
  
  # Group and summarize
  group_by(New_External_ID) %>%
  summarise(
    fulltime = sum(fulltime, na.rm = TRUE),
    parttime = sum(parttime, na.rm = TRUE),
    FTE = fulltime + (parttime * 0.5),
    program_region = first(program_region),
    participated = first(participated),
    years_since_joining = first(years_since_joining),
    post_accelerator = first(post_accelerator),
    year = first(year),
    .groups = "drop"
  )

ggplot(df_emplo %>% 
         filter(!is.na(years_since_joining),
                !is.na(program_region),
                str_to_lower(program_region) != "other"),  # Exclude "other"
       aes(x = years_since_joining, y = FTE, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_continuous(labels = label_comma(), trans = "log10") +  # Log scale
  labs(title = "Empolyess Since Joining (Participated vs Non-Participated)",
       y = "Empolyess",
       x = "Years Since Joining (0 = join year, negative = before joining)",
       color = "Participation Status") +
  scale_color_manual(values = c("steelblue", "Purple"),
                     labels = c("Non-Participant", "Participant")) +
  theme_minimal() +
  facet_wrap(~ program_region, scales = "free_y") +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )


```


```{r}

library(ggplot2)
library(dplyr)
library(stringr)

# Common filter
filtered_df <- df_Invest %>%
  filter(!is.na(years_since_joining),
         !is.na(program_region),
         str_to_lower(program_region) != "other")

# Own Money Invested
ggplot(filtered_df, aes(x = years_since_joining, y = Own, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_log10(labels = scales::label_comma()) +
  labs(
    title = "Own Money Invested in Dollars Since Joining (Participant vs Non-Participant)",
    y = "Own Money Invested",
    x = "Years Since Joining\n(0 = join year, negative = before joining)",
    color = "Participation Status"
  ) +
  scale_color_manual(values = c("steelblue", "Orange"),
                     labels = c("Non-Participant", "Participant")) +
  facet_wrap(~ program_region, scales = "free_y") +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )

# Outequity Earned
ggplot(filtered_df, aes(x = years_since_joining, y = Outequity, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_log10(labels = scales::label_comma()) +
  labs(
    title = "Outequity Earned in Dollars Since Joining (Participant vs Non-Participant)",
    y = "Outequity Earned",
    x = "Years Since Joining\n(0 = join year, negative = before joining)",
    color = "Participation Status"
  ) +
  scale_color_manual(values = c("steelblue", "Purple"),
                     labels = c("Non-Participant", "Participant")) +
  facet_wrap(~ program_region, scales = "free_y") +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )

# Debt
ggplot(filtered_df, aes(x = years_since_joining, y = Debt, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_log10(labels = scales::label_comma()) +
  labs(
    title = "Debt in Dollars Since Joining (Participant vs Non-Participant)",
    y = "Debt",
    x = "Years Since Joining\n(0 = join year, negative = before joining)",
    color = "Participation Status"
  ) +
  scale_color_manual(values = c("steelblue", "red"),
                     labels = c("Non-Participant", "Participant")) +
  facet_wrap(~ program_region, scales = "free_y") +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )

# Philanthropy Earned (with facet by program_region)
ggplot(filtered_df, aes(x = years_since_joining, y = Phil, color = factor(participated))) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_log10(labels = scales::label_comma()) +
  labs(
    title = "Philanthropy Earned in Dollars Since Joining (Participant vs Non-Participant)",
    y = "Philanthropy Earned",
    x = "Years Since Joining\n(0 = join year, negative = before joining)",
    color = "Participation Status"
  ) +
  scale_color_manual(values = c("steelblue", "LightGreen"),
                     labels = c("Non-Participant", "Participant")) +
  theme_minimal() +
  facet_wrap(~ program_region, scales = "free_y") +
  theme(
    strip.text = element_text(size = 10),
    axis.text = element_text(size = 8),
    legend.position = "bottom"
  )

   

```


```{r}
# Load packages (make sure kableExtra is loaded *after* flextable so its footnote() is the one used)
library(dplyr)
library(tibble)
library(lme4)
library(knitr)
library(flextable)
library(kableExtra)

# 1. Gather your models
models <- list(
  Revenue             = model_logREV,
  Wages               = model_logWAG,
  Employees           = model_logEMP1,
  Venture             = model_glm_venture,
  Own_Money_Invested  = model_logOWN,
  `Out Equity`        = model_logOUT,
  Debt                = model_logDEBT,
  Philanthropy        = model_logPhil
)

# 2. Specify variables and labels (in the order you want them shown)
vars <- c(
  "participated1",
  "years_since_joining",
  "program_regionLatin America & Caribbean",
  "program_regionOther",
  "program_regionSouth Asia",
  "program_regionSub-Saharan Africa",
  "(Intercept)"
)
row_name <- c(
  "Participated",
  "Years Since Joining",
  "Region: LAC",
  "Region: Other",
  "Region: South Asia",
  "Region: Sub-Saharan Africa",
  "Intercept"
)

# 3. Cell‐formatting function (handles glm vs. lmer objects, large coefficients, and p‐value/ t‐value stars)
format_cell <- function(m, v) {
  s <- summary(m)$coefficients
  if ("Pr(>|z|)" %in% colnames(s)) {
    est   <- s[v, "Estimate"]
    se    <- s[v, "Std. Error"]
    pval  <- s[v, "Pr(>|z|)"]
    stars <- ifelse(pval < .001, "***",
             ifelse(pval < .01,  "**",
             ifelse(pval < .05,  "*",  "")))
  } else {
    est   <- s[v, "Estimate"]
    se    <- s[v, "Std. Error"]
    tstat <- s[v, "t value"]
    stars <- ifelse(abs(tstat) > 2.576, "***",
             ifelse(abs(tstat) > 1.96,  "**",
             ifelse(abs(tstat) > 1.645, "*", "")))
  }
  # Format big numbers with commas, small with 3 decimals
  if (abs(est) > 1000) {
    est_str <- format(round(est), big.mark = ",")
    se_str  <- format(round(se), big.mark = ",")
  } else {
    est_str <- format(round(est, 3), nsmall = 3)
    se_str  <- format(round(se, 3), nsmall = 3)
  }
  paste0(est_str, stars, " (", se_str, ")")
}

# 4. Build the main body
body <- lapply(models, function(m) {
  vapply(vars, function(v) {
    if (v %in% rownames(summary(m)$coefficients)) {
      format_cell(m, v)
    } else {
      ""
    }
  }, character(1))
}) %>%
  do.call(cbind, .) %>%
  as.data.frame(stringsAsFactors = FALSE)
colnames(body) <- names(models)
body <- cbind(Variable = row_name, body)

# 5. Append footer rows (observations, groups for mixed models, AIC/REML)
obs    <- sapply(models, nobs)
groups <- sapply(models, function(m) {
  if ("lmerMod" %in% class(m)) length(ranef(m)[[1]]) else NA
})
crit   <- sapply(models, function(m) {
  if     ("lmerMod" %in% class(m)) paste0("REML=", format(round(AIC(m)), big.mark = ","))
  else if ("glm"    %in% class(m)) paste0("AIC=",  format(round(AIC(m), 1), big.mark = ","))
  else NA
})
footer <- rbind(
  Observations  = obs,
  `Groups (ID)` = groups,
  `REML/AIC`    = crit
) %>%
  as.data.frame(stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("Variable")

# 6. Stack body + footer
tbl <- bind_rows(body, footer)

# 7. Render with kable + namespaced footnote()
kable(
  tbl,
  row.names = FALSE,
  align    = c("l", rep("c", ncol(tbl)-1)),
  caption  = "Table 2: Estimated Effects of Accelerator Programs on Organizational Growth Indicators",
  booktabs = TRUE
) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  kableExtra::footnote(
    general           = "*** p < 0.001, ** p < 0.01, * p < 0.05",
    general_title     = "",
    footnote_as_chunk = TRUE,
    threeparttable    = TRUE
  )






```



```{r}
# 5. Append only the 'Observations' footer row (no Groups, no REML/AIC)
# 5. Append only the 'Observations' footer row (convert to character to match body)
obs <- sapply(models, nobs)
footer <- rbind(
  Observations = obs
) %>%
  as.data.frame(stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("Variable") %>%
  mutate(across(-Variable, as.character))


# 6. Stack body + footer
tbl <- bind_rows(body, footer)

# 6.1 Rename "Venture" to "VC Transition" in column names
colnames(tbl) <- sub("^Venture$", "Equity from VCs ", colnames(tbl))

# 7. Render with kable + namespaced footnote()
kable(
  tbl,
  row.names = FALSE,
  align    = c("l", rep("c", ncol(tbl)-1)),
  caption  = "Table 2: Estimated Effects of Accelerator Programs on Organizational Growth Indicators",
  booktabs = TRUE
) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  kableExtra::footnote(
    general           = "*** p < 0.001, ** p < 0.01, * p < 0.05",
    general_title     = "",
    footnote_as_chunk = TRUE,
    threeparttable    = TRUE
  )


```










```{r}
#Summary stats of the whole code: Using psych for detailed descriptive statistics for a clean metrics like mean, standard deviation, skewness, and kurtosis.
library(psych)
describe(Gali_data)
library(dplyr)

# Perform t-test by year, region, and participation group on Gali_data
t_test_results <- Gali_data %>%
  filter(
    program_year >= 2013 & program_year <= 2019,
    program_region %in% c("Latin America & Caribbean", "North America", "Sub-Saharan Africa", "South Asia")
  ) %>%
  pivot_longer(
    cols = where(is.numeric) & !c("participated", "program_year"),
    names_to = "variable",
    values_to = "value"
  ) %>%
  group_by(program_year, program_region, variable) %>%
  do({
    if(length(unique(.$participated)) == 2) {
      var_0 <- var(.$value[.$participated == 0], na.rm = TRUE)
      var_1 <- var(.$value[.$participated == 1], na.rm = TRUE)
      
      if(!is.na(var_0) & !is.na(var_1) & var_0 > 0 & var_1 > 0) {
        t_test_result <- t.test(value ~ participated, data = .)
        data.frame(
          program_year = unique(.$program_year),
          program_region = unique(.$program_region),
          variable = unique(.$variable),
          t_statistic = t_test_result$statistic,
          df = t_test_result$parameter,
          p_value = t_test_result$p.value,
          conf_low = t_test_result$conf.int[1],
          conf_high = t_test_result$conf.int[2]
        )
      } else {
        data.frame(
          program_year = unique(.$program_year),
          program_region = unique(.$program_region),
          variable = unique(.$variable),
          t_statistic = NA, df = NA, p_value = NA, conf_low = NA, conf_high = NA
        )
      }
    } else {
      data.frame(
        program_year = unique(.$program_year),
        program_region = unique(.$program_region),
        variable = unique(.$variable),
        t_statistic = NA, df = NA, p_value = NA, conf_low = NA, conf_high = NA
      )
    }
  }) %>%
  ungroup()

# View the results
View(t_test_results)





```



```{r}
# Compute descriptive statistics
library(psych)
describe(Gali_data)
library(dplyr)
desc_stats <- describe(Gali_data) %>%
  tibble::rownames_to_column("variable") %>%  # Convert row names to column for merging
  select(variable, n, mean, sd, median, min, max, skew, kurtosis, se)  # Select relevant stats

# Merge descriptive statistics with t-test results
combined_results <- t_test_results %>%
  left_join(desc_stats, by = "variable")

# View the combined results
View(combined_results)

library(writexl)  # For saving as Excel
library(readr)    # For saving as CSV

write.csv(combined_results, file = "~/Desktop/combined_results3.csv")



```



```{r}
library(psych)
library(dplyr)
library(tidyr)


desc_stats <- Gali_data %>%
  filter(
    program_year >= 2013 & program_year <= 2019,
    program_region %in% c("Latin America & Caribbean", "North America", "Sub-Saharan Africa", "South Asia","Other")
  ) %>%
  select(where(is.numeric), program_year, program_region) %>%
  pivot_longer(
    cols = -c(program_year, program_region),
    names_to = "variable",
    values_to = "value"
  ) %>%
  group_by(program_year, program_region, variable) %>%
  filter(!all(is.na(value))) %>%
  summarise(
    n = round(sum(!is.na(value)), 3),
    mean = round(mean(value, na.rm = TRUE), 3),
    sd = round(sd(value, na.rm = TRUE), 3),
    median = round(median(value, na.rm = TRUE), 3),
    min = round(min(value, na.rm = TRUE), 3),
    max = round(max(value, na.rm = TRUE), 3),
    skew = round(psych::skew(value, na.rm = TRUE), 3),
    kurtosis = round(psych::kurtosi(value, na.rm = TRUE), 3),
    se = round(sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))), 3),
    .groups = "drop"
  )

```



```{r}
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)

# Define group labels and custom order
group_labels <- c(
  "participated" = "Accelerated",
  "2013 (0/1)" = "Application year", "2014 (0/1)" = "Application year", 
  "2015 (0/1)" = "Application year", "2016 (0/1)" = "Application year",
  "2017 (0/1)" = "Application year", "2018 (0/1)" = "Application year",
  "2019 (0/1)" = "Application year",
  "impact_area_agprod" = "Operating sector",
  "impact_area_health" = "Operating sector",
  "impact_area_fueleff" = "Operating sector",
  "impact_area_other" = "Operating sector",
  "found_name1_education" = "Team education",
  "model_has_copyrights" = "Intellectual capital",
  "model_has_patents" = "Intellectual capital",
  "model_has_trademarks" = "Intellectual capital",
  "report_any_prior_accelerator" = "Prior accelerator experience",
  "found_name1_gender" = "Team gender composition",
  "found_name2_gender" = "Team gender composition",
  "found_name3_gender" = "Team gender composition",
  "inv_hasequity" = "Traction", "inv_hasdebt" = "Traction", "inv_hasphilan" = "Traction",
  "fins_ft_employees_m1" = "Traction", "fins_revenues_m1" = "Traction",
  "fins_profit_m1" = "Traction", "fins_pt_employees_m1" = "Traction",
  "Latin America & Caribbean (0/1)" = "Program region",
  "North America (0/1)" = "Program region", "South Asia (0/1)" = "Program region",
  "Sub-Saharan Africa (0/1)" = "Program region", "Others (0/1)" = "Program region"
)

variable_order <- c(
  "participated",
  "2013 (0/1)", "2014 (0/1)", "2015 (0/1)", "2016 (0/1)", "2017 (0/1)", "2018 (0/1)", "2019 (0/1)",
  "impact_area_agprod", "impact_area_health", "impact_area_fueleff", "impact_area_other",
  "found_name1_education",
  "model_has_copyrights", "model_has_patents", "model_has_trademarks",
  "report_any_prior_accelerator",
  "found_name1_gender", "found_name2_gender", "found_name3_gender",
  "inv_hasequity", "inv_hasdebt", "inv_hasphilan",
  "fins_ft_employees_m1", "fins_revenues_m1", "fins_profit_m1", "fins_pt_employees_m1",
  "Latin America & Caribbean (0/1)", "North America (0/1)", "South Asia (0/1)",
  "Sub-Saharan Africa (0/1)", "Others (0/1)"
)

# Combine and organize the data
summary_output <- bind_rows(dummy_summary, non_dummy_summary) %>%
  mutate(
    Description = ifelse(variable %in% var_list,
                         var_desc[match(variable, var_list)],
                         variable),
    Group = group_labels[variable],
    variable = factor(variable, levels = variable_order)
  ) %>%
  arrange(Group, variable) %>%
  group_by(Group) %>%
  mutate(Group = ifelse(row_number() == 1, Group, NA)) %>%  # Keep group name only for the first row in each group
  ungroup() %>%
  fill(Group, .direction = "down") %>%  # Fill group names down for other rows
  select(Group, variable, Description, N, Mean, SD)

# Create the table with grouped headers
summary_output %>%
  kable(caption = "Descriptive Statistics of Selected Variables", format = "markdown") %>%
  kable_styling(full_width = FALSE, 
                font_size = 12) %>%
  column_spec(1, width = "3cm")  # Adjust the width of the first column to fit the group names


```



participated	Indicates ventures that finished the full program
program_region	Region (World Bank definition) where the accelerator program took place
program_year	Program year
model_has_patents	Have patents	Whether assigned by an owner or obtained in some other way, does your venture have any of the following? (check all that apply) - Patents
model_has_trademarks	Have trademarks	Whether assigned by an owner or obtained in some other way, does your venture have any of the following? (check all that apply) - Trademarks
model_has_copyrights	Have copyrights	Whether assigned by an owner or obtained in some other way, does your venture have any of the following? (check all that apply) - Copyrights
inv_hasdebt	Venture has debt	Please indicate whether your venture has received any of the / following investments from outside s...-Debt (not including any personal debt obtained on behalf of the business)
inv_hasequity	Venture has equity	Please indicate whether your venture has received any of the / following investments from outside s...-Equity (equity investment is money received in return for some portion of ownership)
inv_hasphilan	Venture has philanthropy	Please indicate whether your venture has received any of the / following investments from outside s...-Philanthropy (e.g., seed grants, awards, or donations)
impact_area_health	Impact area: Health improvement	Which of the following impact objectives does your venture currently seek to address? (check up to three) - Health improvement
impact_area_agprod	Impact area: Agriculture productivity	Which of the following impact objectives does your venture currently seek to address? (check up to three) - Agriculture productivity
impact_area_information	Impact area: Access to information	Which of the following impact objectives does your venture / currently seek to address? (check up t...-Access to information
impact_area_other	Impact area: Other	Which of the following impact objectives does your venture currently seek to address? (check up to three) - Other
fins_ft_employees_m1	Number of full time employees in Year t-1	Not counting founders, on December 31, ${e://Field/yearm1}, how many people worked / for your venture?  /  /  (please exclude contract workers /  who are not on the business' official payroll)-Full-time employees
fins_profit_m1	Profit margin in Year t-1	Profit is the business' income after all expenses and taxes have / been deducted. Roughly speaking, what was your venture's profit / margin (as a percentage of total investment) for calendar year ${e://Field/yearm1}? 
fins_pt_employees_m1	Number of part time employees	Not counting founders, on December 31, ${e://Field/yearm1}, how many people worked / for your venture?  /  /  (please exclude contract workers /  who are not on the business' official payroll)-Part-time employees
fins_revenues_m1	Revenue in Year t-1	What was your venture's total earned revenue: /  (please do not include any /  philanthropic investments or donations in this /  amount)-in calendar year ${e://Field/yearm1}? ($US)
found_name1_education	Founder 1 highest level of education completed	Now, please provide the following information about each of the three founders listed above: - Founder 1 Highest Level of Education Completed
found_name1_gender	Founder 1 gender	Now, please provide the following information about each of the three founders listed above: - Founder 1 Gender
found_name2_education	Founder 2 highest level of education completed	Now, please provide the following information about each of the three founders listed above: - Founder 2 Highest Level of Education Completed
found_name2_gender	Founder 2 gender	Now, please provide the following information about each of the three founders listed above: - Founder 2 Gender

found_name3_education	Founder 3 highest level of education completed	Now, please provide the following information about each of the three founders listed above: - Founder 3 Highest Level of Education Completed


```{r}
# Summarize and filter top 15 most valuable variables from combined_results
# Identify top 15 variables by average absolute t-statistic

# Step 1: Filter combined results to only include rows where p_value < 0.05
significant_data <- combined_results %>%
  filter(!is.na(t_statistic), p_value < 0.05)  # Keep only rows with p_value < 0.05

# Step 2: Get the list of variables that are statistically significant
significant_vars <- significant_data %>%
  group_by(variable) %>%
  summarise(
    avg_abs_t = mean(abs(t_statistic), na.rm = TRUE),
    avg_p_value = mean(p_value, na.rm = TRUE),
    n_years_significant = n()
  ) %>%
  arrange(desc(avg_abs_t)) %>%
  pull(variable)

# Step 3: Filter the original data to only include significant variables
top_combined_results <- significant_data %>%
  filter(variable %in% significant_vars)

# View results
View(top_combined_results)


top_results_table <- top_combined_results %>%
  filter(variable %in% significant_vars[1:10]) %>%  # Optional: top 10 variables based on T-statistic
  group_by(program_year) %>%  # Group by year
  slice_max(order_by = abs(t_statistic), n = 2) %>%  # Select the top 2 variables by absolute t-statistic
  rename(
    "Variable" = variable,
    "Year" = program_year,
    "T-Statistic" = t_statistic,
    "P-Value" = p_value,
    "Mean" = mean,
    "SD" = sd
  ) %>%
  mutate(`P-Value` = round(`P-Value`, 3)) %>%  # Round p-values
  select(Year, Variable, `T-Statistic`, `P-Value`, Mean, SD, n)  # Select relevant columns



# Make sure you have kableExtra installed
library(knitr)
library(kableExtra)

# Create the table
kable(top_results_table, format = "markdown", digits = 3, caption = " Table 1: Top 2 Most Statistically Significant Gali Variables Per Year") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(1, bold = TRUE) %>%  # Bold Year column
  column_spec(2, bold = TRUE) %>%  # Bold Variable column
  column_spec(3, color = "red") %>%  # Highlight T-Statistic in red (just as an example)
  column_spec(4, color = "blue") %>%  # Highlight P-Value in blue
  row_spec(0, bold = TRUE, background = "lightgray")  # Bold headers and light gray background for header row

```


